### 2018-06-29 paper/1-intro.tex
Work on abstract and intro

\item We show that we can instantiate
our abstractions to describe the essence of a variety of different
real-life build systems, including \Make, \Shake, \Bazel, and \Excel, each in
a dozen lines of code or so (\S\ref{sec-implementations}).
Doing this modelling in a single setting allows
the differences and similarities between these huge systems to be
brought out clearly.

\item Moreover, we can readily remix the ingredients to describe the first
  build system that supports both \emph{dynamic dependencies}
  and \emph{cloud build} (\S\ref{sec-implementation-cloud}).

>>>>

\item We show that we can instantiate our abstractions to describe the essence
of a variety of different real-life build systems, including \Make, \Shake,
\Bazel, \CloudBuild, \Buck, \Nix, and \Excel, each in a dozen lines of code
or so (\S\ref{sec-implementations}). Doing this modelling in a single setting
allows the differences and similarities between these huge systems to be
brought out clearly.

\item Moreover, we can readily remix the ingredients to design new build systems
with desired properties, for example, to combine the advantages of \Shake and
\Bazel (\S\ref{sec-implementation-cloud}).
